Cover Letter

### 2017-12-13 paper/cover_letter.tex
paper: experimental setup, popper (#27, #30)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>
paper: fix graphs and add baselines (#33, #34)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{red}{\textbf{red}} and deletions in
\textcolor{blue}{\textbf{blue}}. Three issues were common across reviewer
feedback:

%Experimental Setup (R1, R2, R3)
%- code R1
%- servers, network, storage R1, R3
\section{No Experimental Setup (Reviewers 1, 2, and 3)}

We apologize for the omission of experimental setup and source code details.
For the experimental setup, we have added details about the cluster we ran on
in Table III as well as a description in the text (addresses Reviewers 1 and
3). For the source code, we have added code snippets to the Evaluation to
concretize what was actually done (addresses Reviewer 1).

Additionally, we have added paper artifacts online.  For the experimental
setup, we have made the infrastructure code available and added links after
each figure to show exactly how experiments are run.  This infrastructure code
contains scripts to deploy the system, run experiments, and gather results.
This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  We also make the source code available and
linked in the paper.

%Mixing contributions and future work (R1)
%Statements in Introduction do not align with Evaluation (R1, R2, R3)
%- quantify performance speedups R3
%Evaluation Structure (R2)
%- remove major takeaways and cross refercnes
%Will not address:
%- cost of dynamically changing consistency/durability not presented R1
\section{Structure and Layout of Evaluation (All Reviewers)}

One pervasive issue across reviews is that the results and contributions we
cite in the introduction are not validated, explained, or even mentioned in the
Evaluation.  To fix this, we separate out future work to make the contributions
of this paper more explicit (addresses Reviewer 1) and we connect all numbers
we cite in the introduction to the evaluation (addresses all reviewers).  To
further clarify the Evaluation, we:

@@

  \item added Table IV which includes raw baseline, Cudele, and hardware limit
numbers. This adds raw numbers and helps us make comparisons to hardware
speeds. Ultimately, we hope this adds insight into the results (addresses
Reviewers 2 nad 3).

  \item re-organized the section to make experiments more independent
and removed cross-references (addresses Reviewer 2). Experiments are now
self-contained so the reader can see the effects of different API
configurations (addresses Reviewer 2) and we do a better job of explaining how
results are derived (addresses Reviewer 3).

  \item removed the ``major takeaways". We deleted the headings but left the
conclusions we make as transitions (Reviewer 2). We also add insights into the
results by analyzing the raw numbers we observe.

@@

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section{Synthetic and/or Irrelevant Use Cases (Reviewers 2 and 4)}

We add a section to the introduction that scopes the importance of storage for
large scale runtimes and workflows. Parallel and distributed jobs (whether that
be MPI-based or more structured runtimes like Hadoop) need parallel and
distributed storage systems that keep up with the computation. Furthermore, we
highlight the parallel and distributed computing themes (addresses Reviewer 4)
and cast light on them from the context of our prototype. We also add the Spark
discussion proposed by Reviewer 2 to the Evaluation. The goal is to show how a
system such as Cudele would benefit more general runtimes. We also move the
discussion about the potential for HDFS and CephFS subtrees in the same
namespace and the cost of dynamically changing consistency and durability
semantics on a subtree.

\section*{Cosmetic Fixes}
%Terminology
%- users vs. clients R2

>>>>

We thank the reviewers for their hard work and genuinely helpful suggestions.
In addition to this cover letter, we have posted a PDF online explicitly
showing additions in \textcolor{red}{\textbf{red}} and deletions in
\textcolor{blue}{\textbf{blue}}. Three issues were common across reviewer
feedback; Reviewer 1 and 3's comments are addressed in issues I and II,
Reviewer 2's comments are addressed in issues I and III, and Reviewer 4's
comments are addressed in issues II and III.

%Experimental Setup (R1, R2, R3)
%- code R1
%- servers, network, storage R1, R3
\section*{Issue I: No Experimental Setup (Reviewers 1, 2, and 3)}

We apologize for the omission of experimental setup and source code details. To
provide a more comprehensive view of our experiments, we added text to the
paper and made paper artifacts available online. For the experimental setup, we
describe the cluster setup (hardware, software, etc.) in Section~{\S}V.  We
have also made the infrastructure code available and added links after each
figure to show exactly how experiments are run.  This infrastructure code
contains scripts to deploy the system, run experiments, and gather results.
This process follows the Popper
Convention\footnote{http://falsifiable.us/}~\cite{jimenez_popper_2016}, which
aims to make research reproducible.  For the source code, we have added code
snippets to the evaluation to concretize what was actually done and made the
source code available online. A link is provided in a footnote in
Section~{\S}V.

%Mixing contributions and future work (R1)
%Statements in Introduction do not align with Evaluation (R1, R2, R3)
%- quantify performance speedups R3
%Evaluation Structure (R2)
%- remove major takeaways and cross refercnes
%Will not address:
%- cost of dynamically changing consistency/durability not presented R1
\section*{Issue II: Structure and Layout of Evaluation (All Reviewers)}

All reviewers note that the results and contributions we cite in the
introduction are not validated, explained, or even mentioned in the evaluation.
One confusing component of this issue is that we mixed future work with the
contributions of this paper; to make the contributions more explicit we remove
future work from the introduction and add it to the future work section in
Section~{\S}VI. We also connect all numbers we cite in the introduction to the
evaluation. To further clarify the evaluation, we:

@@

  \item added raw numbers (as annotations) to the baselines in each figure.
This helps the reader calculate the raw numbers instead of just relying on
overhead and speedup numbers.

  \item re-organized the section to make experiments more independent and
removed cross-references. Experiments are now self-contained so the reader can
see the effects of different API configurations and we do a better job of
explaining how results are derived.

  \item removed the ``major takeaways". We deleted the headings but left the
conclusions we make as transitions. We also add insights into the results by
analyzing the raw numbers we observe in comparison to hardware capabilities.

@@

%Use Cases R2, R4
%- Spark discussion R2
%- more emphasis on parallel and distributed computing themes R4
\section*{Issue III: Synthetic and/or Irrelevant Use Cases (Reviewers 2 and 4)}

We add a section to the introduction that scopes the importance of storage for
large scale runtimes and workflows. Parallel and distributed jobs (whether they
are MPI-based, MapReduce-based, etc.) need parallel and distributed storage
systems that keep up with the computation. Furthermore, we highlight the
parallel and distributed computing themes and cast light on them from the
context of our prototype. We also add the Spark discussion proposed by to the
evaluation. The goal is to show how a system such as Cudele would benefit from
more general runtimes. We also move the discussion about the potential for HDFS
and CephFS subtrees in the same namespace and the cost of dynamically changing
consistency and durability semantics on a subtree.

\section*{Cosmetic Fixes}
%Terminology
%- users vs. clients R2
\begin{itemize}
  \item Reviewer 1: fixed user vs. client terminology in Section~{\S}III
  \item Reviewer 1: clarified that the cost of dynamically changing semantics is future work Sections~{\S}III and ~{\S}V.E
  \item Reviewer 1: added source code pointer in Section~{\S}IV
  \item Reviewer 2: remove major takeways in Section~{\S}V
  \item Reviewer 2: remove major cross-references in Section~{\S}V
  \item Reviewer 3: quantified speedups with figure annotations in Section~{\S}V
  \item Reviewers 1 and 3: add servers, network, and storage setups in Section~{\S}V
  \item Reviewer 4: add new section ({\S}V.F) describing how Cudele would work with a system like Spark
\end{itemize}

### 2017-12-13 paper/sections/1_introduction.tex
paper: fix graphs and add baselines (#33, #34)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The last contribution lays the groundwork for future work on our prototype. It
is more scalable than the current practice of mounting different storage systems in a global
namespace because there is no need to provision dedicated storage clusters to
applications or move data between these systems.  For example, the results of a
Hadoop job do not need to be migrated into a Ceph file system (CephFS) for other processing; instead
the user can change the semantics of the HDFS subtree into a CephFS subtree.
This may cause metadata/data movement to make things strongly consistent again
but this is superior to moving all data across file system boundaries. Our prototype
enables studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.

>>>>

\oldcomment{The last contribution lays the groundwork for future work on our
prototype. It is more scalable than the current practice of mounting different
storage systems in a global namespace because there is no need to provision
dedicated storage clusters to applications or move data between these systems.
For example, the results of a Hadoop job do not need to be migrated into a Ceph
file system (CephFS) for other processing; instead the user can change the
semantics of the HDFS subtree into a CephFS subtree.  This may cause
metadata/data movement to make things strongly consistent again but this is
superior to moving all data across file system boundaries. Our prototype
enables studies that adjust these semantics over {\it time and space}, where
subtrees can change their semantics and migrate around the cluster without ever
moving the data they reference.}

### 2017-12-13 paper/sections/6_results.tex
paper: fix graphs and add baselines (#33, #34)
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
Performance of each mechanism (left) and building the consistency/durability
semantics of real-world systems (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.  \label{fig:composable-mechanisms}}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
      Use Case 1} \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
      Use Case 2} \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{
      [\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
      Use Case 3} \label{fig:slowdown-sync}
  \end{subfigure}
\caption{
The performance and features of Cudele. (a) shows the cost of merging client
journals at the metadata server. Shipping and merging journals of updates
scales better than RPCs because there are less messages and
consistency/durability code paths are bypassed. In (b), the allow/block API
isolates directories from interfering clients. (c) is the slowdown of a single
client syncing updates to the global namespace. The inflection point is the
trade-off of frequent updates vs. larger journal files.\label{fig:use-cases}}
\end{figure*}

@@

>>>>

\subsection{Microbenchmarks}
\label{sec:microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/composable-mechanisms.png}
\caption{
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mechanisms/visualize/viz.ipynb}{source}]
\newcomment{Overhead of processing 100K events for each mechanism in
Table~\ref{table:mechanisms}. Results are normalized to the runtime of writing
events to client memory. The bars on the far right show the overhead of
building consistency/durability semantics of real world systems.}
\oldcomment{Performance of each mechanism (left) and building the consistency/durability
semantics of real-world systems (right) for 100K files creates from a single
client. Results are normalized to the runtime of writing events to the client's
in-memory journal.}\label{fig:composable-mechanisms}}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/mergescale.png}
      \caption{\texttt{create}: done in parallel on clients}
      \label{fig:mergescale}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/block-allow.png}
      \caption{Subtree semantics: block interference}
      \label{fig:block-allow}
  \end{subfigure}
  \begin{subfigure}[b]{.3\linewidth}
      \centering
      \includegraphics[width=1.0\linewidth]{graphs/slowdown-sync.png}
      \caption{Syncing to global namespace}
      \label{fig:slowdown-sync}
  \end{subfigure}
\caption{ The performance and features of Cudele. (a)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-mergescale/visualize/viz.ipynb}{source}]
shows the cost of merging client journals at the metadata server. Shipping and
merging journals of updates scales better than RPCs because there are less
messages and consistency/durability code paths are bypassed. (b)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-blockapi/visualize/viz.ipynb}{source}]
the allow/block API isolates directories from interfering clients. (c)
[\href{https://github.com/michaelsevilla/cudele-popper/blob/revision/experiments/cudele-partialreads/visualize/viz.ipynb}{source}]
is the slowdown of a single client syncing updates to the global namespace. The
inflection point is the trade-off of frequent updates vs. larger journal
files.} \label{fig:use-cases}
\end{figure*}

@@

\newcomment{We have shown that our API and framework is an effective
abstraction for letting users custom fit subtrees to applications.  It is more
scalable than the current practice of mounting different storage systems in a
global namespace because there is no need to provision dedicated storage
clusters to applications or move data between these systems.  For example, the
results of a Hadoop job do not need to be migrated into a Ceph file system
(CephFS) for other processing; instead the user can change the semantics of the
HDFS subtree into a CephFS subtree.  This may cause metadata/data movement to
make things strongly consistent again but this is superior to moving all data
across file system boundaries. Our prototype enables studies that adjust these
semantics over {\it time and space}, where subtrees can change their semantics
and migrate around the cluster without ever moving the data they reference.}
